### 2018-04-30 paper/evaluation.tex
details on plots

>>>>

In figure \ref{fig:nodes_per_layer_vs_theta} and \ref{fig:success_rate_vs_t}, we computed 10 experiments per set of settings.
$\theta$ is the threshold of the probability that all nodes fail at once: we keep adding nodes to a layer until the layer's probability is below $\theta$. 
It takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
$L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
The time since route establishment goes from 1 to 10 with  unit step. 
An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
Hence, each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the average of 3000 layers size; 
each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the availability rate over 200 routes.
